---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# bellreg

<!-- badges: start -->
[![R build status](https://github.com/fndemarqui/bellreg/workflows/R-CMD-check/badge.svg)](https://github.com/fndemarqui/bellreg/actions)
[![CRAN_Status_Badge](https://www.r-pkg.org/badges/version/bellreg)](https://cran.r-project.org/package=bellreg)
[![Downloads](https://cranlogs.r-pkg.org/badges/bellreg)](https://cran.r-project.org/package=bellreg)
[![Total Downloads](https://cranlogs.r-pkg.org/badges/grand-total/bellreg?color=orange)](https://cran.r-project.org/package=bellreg)
<!-- badges: end -->

The goal of bellreg is to provide a set of functions to fit  regression models for count data with overdispersion using the Bell distribution. The implemented models account for ordinary and zero-inflated regression models under both frequentist and Bayesian approaches. Theoretical details regarding the models implemented in the package can be found in Castellares et al. (2018) <doi:10.1016/j.apm.2017.12.014> and Lemonte et al. (2020) <doi:10.1080/02664763.2019.1636940>. 

## Installation

You can install the development version of bellreg from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("fndemarqui/bellreg")
```

## Example


```{r example}
library(bellreg)

data(faults)

# ML approach:
mle <- bellreg(nf ~ lroll, data = faults, approach = "mle", init = 0)
summary(mle)

# Bayesian approach:
bayes <- bellreg(nf ~ lroll, data = faults, approach = "bayes", refresh = FALSE)
summary(bayes)

```
